SubsidyExplorer - Step 6: Run Model

### 2020-09-02 scripts/06_run_model.Rmd
updating global results

title: "SubsidyExplorer - Step 6: Run Model"
author: "Kat Millage, Vienna Saccomanno, Laura Lea Rubino, Christopher Costello"
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
bibliography: "../pew-subsidies.bib"
---

@@

# Directories for the output files generated by this script
results_dir <- here::here("results", "06-run-model/")
if (dir.exists(results_dir) == F) {
  dir.create(results_dir, recursive = T)
}
```

# Introduction

This script generates the most ambitious global and regional results obtained by removing all capacity enhancing subsidies from all WTO Members and Observers.

```{r}
# Source model script
source(here::here("app", "scripts", "BioEconModel.R"))
```

@@

## Create global fleet

```{r pressure, echo=FALSE}
# Assign fleets to vessels
global_fleet_vessels <- vessel_dat %>%
  left_join(country_dependencies %>% dplyr::select(iso3, is_WTO), by = c("flag_iso3" = "iso3")) %>%
  mutate(fleet = case_when(is_WTO & fmi_best >= managed_cutoff & bad_subs > 0 ~ "affected_managed",
                           is_WTO & fmi_best < managed_cutoff & bad_subs > 0 ~ "affected_oa",
                           (!is_WTO & fmi_best >= managed_cutoff) ~ "unaffected_managed",
                           (!is_WTO & fmi_best < managed_cutoff) ~ "unaffected_oa",
                           TRUE ~ "unaffected_oa"))
```

## Run Model (Remove all bad subsidies)

```{r}
# Create model input for removing all bad subsidies
global_all_bad_summary <- global_fleet_vessels %>%
  group_by(region, fleet) %>%
  summarize(catch = sum(catch, na.rm = T),
            bad_subs = sum(bad_subs, na.rm = T),
            fishing_KWh = sum(fishing_KWh_eez_fao_ter, na.rm = T),
            removed_subs = sum(bad_subs, na.rm = T)) %>%
  ungroup()

# Turn into a list
global_all_bad_list <- global_all_bad_summary %>%
  group_by(region) %>%
  group_split()
names(global_all_bad_list) <- colnames(bio_dat_regional)[-c(1:2)]

# Run model
global_all_bad_results <- pmap_df(list(fleet = global_all_bad_list, 
                                       region = names(global_all_bad_list),
                                       bio_param = bio_dat_regional_list),
                                  BioEconModel,
                                  end_year = 2100,
                                  return = "all")

# Extract results timeseries
global_all_bad_results_full <- global_all_bad_results %>%
  dplyr::filter(Year > 2018) %>%
  dplyr::filter(Variable %in% c("biomass", "catches_total", "revenue_total")) %>%
  group_by(Year, Variable, Fleet) %>%
  mutate(Diff = case_when(BAU != 0 ~ (Reform - BAU)/abs(BAU),
                          TRUE ~ 0),
         BAU_global = sum(BAU, na.rm = T),
         Reform_global = sum(Reform, na.rm = T),
         Diff_global = case_when(BAU_global != 0 ~ (Reform_global - BAU_global)/abs(BAU_global),
                                 TRUE ~ 0)) %>%
  ungroup() %>%
  mutate(run_number = "A",
         run_name = "Most ambitious scenario",
         id = "A",
         Description = "Complete removal of all capacity-enhancing subsidies (for comparison)")

# Extract ending results (difference only)
global_all_bad_results_last <- global_all_bad_results_full %>%
  dplyr::filter(Year == 2100) %>%
  group_by(Year, Variable) %>%
  summarize(Value = unique(Diff_global)*100) %>%
  ungroup() %>%
  spread(Variable, Value) %>%
  rename(Biomass = biomass,
         Catches = catches_total,
         Revenue = revenue_total) %>%
  mutate(run_number = "A",
         run_name = "Most ambitious scenario")

```

@@

  # 1) global (aggregated) timeseries plot
  global_all_bad_plot <- global_all_bad_results_full %>%
        group_by(run_number, run_name, id, Year, Variable, Fleet) %>%
        summarize(BAU = unique(BAU_global),
                  Reform = unique(Reform_global),
                  Diff = unique(Diff_global)) %>%
        ungroup() %>%
        mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
                                    Variable == "catches_total" ~ "Catches",
                                    Variable == "revenue_total" ~ "Revenue")) %>%
        mutate(Region = "Global") %>%
        ggplot()+
        aes(x = Year, y = Diff*100, color = Variable)+
        geom_line(size = 1)+
        theme_bw()+
        geom_hline(yintercept = 0)+
        scale_x_continuous(expand = c(0,0))+
        labs(x = "Year", y = "Change relative to BAU (%)")+
        theme(legend.position = "none")+
        facet_wrap(~Variable, ncol = 1, scales = "free_y")

  ggsave(paste0(results_dir, "global_all_bad_timeseries_plot.png"), global_all_bad_plot, width = 7.5, height = 6, units = "in")

  # 2) regional timeseries plot
  regional_all_bad_plot <- global_all_bad_results_full %>%
        dplyr::select(run_number, run_name, id, Year, Variable, Fleet, Region, BAU, Reform, Diff) %>%
        mutate(Region = case_when(Region == "atlantic" ~ "Atlantic Ocean",
                                  Region == "indian" ~ "Indian Ocean",
                                  Region == "pacific" ~ "Pacific Ocean")) %>%
        mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
                                    Variable == "catches_total" ~ "Catches",
                                    Variable == "revenue_total" ~ "Revenue")) %>%
        ggplot()+
        aes(x = Year, y = Diff*100, color = Variable)+
        geom_line(size = 1)+
        theme_bw()+
        geom_hline(yintercept = 0)+
        scale_x_continuous(expand = c(0,0))+
        labs(x = "Year", y = "Change relative to BAU (%)")+
        theme(legend.position = "none")+
        facet_wrap(Variable ~ Region, ncol = 3, scales = "free_y")

  ggsave(paste0(results_dir, "regional_all_bad_timeseries_plot.png"), regional_all_bad_plot, width = 7.5, height = 6, units = "in")

}
```

>>>>

title: "SubsidyExplorer - Step 6: Run Model"
author: "Kat Millage, Vienna Saccomanno, Laura Lea Rubino, Christopher Costello"
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
bibliography: "../pew-subsidies.bib"
---
# Introduction

This script generates alternative global and regional results.

@@

# Directories for the output files generated by this script
results_dir <- here::here("results", "06-run-model/")
if (dir.exists(results_dir) == F) {
  dir.create(results_dir, recursive = T)
}

bad_subsidy_types <- c("B1", "B2", "B3", "B4", "B5", "B6", "B7")
ugly_subsidy_types <- c("C1", "C2", "C3")
```

```{r}
# Source model script
source(here::here("app", "scripts", "BioEconModel.R"))

# Source plotting script
source(here::here("scripts", "functions", "BioEconomicModelPlots.R"))
```

@@

```{r pressure, echo=FALSE}
# Assign fleets to vessels
fleet_vessels <- vessel_dat %>%
  left_join(country_dependencies %>% dplyr::select(iso3, is_WTO), by = c("flag_iso3" = "iso3")) %>%
  mutate(fleet = case_when(is_WTO & fmi_best >= managed_cutoff & bad_subs > 0 ~ "affected_managed",
                           is_WTO & fmi_best < managed_cutoff & bad_subs > 0 ~ "affected_oa",
                           (!is_WTO & fmi_best >= managed_cutoff) ~ "unaffected_managed",
                           (!is_WTO & fmi_best < managed_cutoff) ~ "unaffected_oa",
                           TRUE ~ "unaffected_oa")) %>%
    mutate(bad_ugly_subs = rowSums(select(., one_of(paste0(c(bad_subsidy_types, ugly_subsidy_types), "_subs")))))
```

# Section 1: Absolute subsidy values

This first section presents results obtained by using absolute subsidy values.

## Scenario 1: Remove all bad + ugly

```{r}
# Create model input for removing all bad subsidies
abs_all_BC_fleet_summary <- fleet_vessels %>%
  group_by(region, fleet) %>%
  summarize(catch = sum(catch, na.rm = T),
            bad_subs = sum(bad_ugly_subs, na.rm = T),
            fishing_KWh = sum(fishing_KWh_eez_fao_ter, na.rm = T),
            removed_subs = sum(bad_ugly_subs, na.rm = T)) %>%
  ungroup()

# Turn into a list
abs_all_BC_list <- abs_all_BC_fleet_summary %>%
  group_by(region) %>%
  group_split()
names(abs_all_BC_list) <- colnames(bio_dat_regional)[-c(1:2)]

# Run model
abs_all_BC_results <- pmap_df(list(fleet = abs_all_BC_list, 
                                       region = names(abs_all_BC_list),
                                       bio_param = bio_dat_regional_list),
                                  BioEconModel,
                                  end_year = 2100,
                                  return = "all")

# Extract results timeseries
abs_all_BC_results_all <- abs_all_BC_results %>%
  dplyr::filter(Year > 2018) %>%
  group_by(Year, Variable, Fleet) %>%
  mutate(Diff = case_when(BAU != 0 ~ (Reform - BAU)/abs(BAU),
                          TRUE ~ 0)) %>%
  ungroup() %>%
  mutate(run_id = "Absolute",
         run_name = "All subsidies")

write_csv(abs_all_BC_results_all, paste0(results_dir, "abs_subs_all_BC_ts.csv"))
```

@@

  # 1) global (aggregated) timeseries plot
  abs_all_BC_ts_plot <- BioEconomicModelPlots(dat = abs_all_BC_results_all,
                                              spatial_res = "global",
                                              temporal_res = "all",
                                              start_year = 2018,
                                              end_year = 2100,
                                              plot_name = "abs_all_BC_ts_plot",
                                              plot_width = 8,
                                              plot_height = 6.5,
                                              results_dir = results_dir)

  # 2) global (aggregated) "kobe" final year plot
  abs_all_BC_end_plot <- BioEconomicModelPlots(dat = abs_all_BC_results_all,
                                                      spatial_res = "global",
                                                      temporal_res = "last",
                                                      end_year = 2100,
                                                      plot_name = "abs_all_BC_end_plot",
                                                      plot_width = 8,
                                                      plot_height = 6.5,
                                                      results_dir = results_dir)

  # 3) regional timeseries plot
  regional_abs_all_BC_ts_plot <- BioEconomicModelPlots(dat = abs_all_BC_results_all,
                                                      spatial_res = "regional",
                                                      temporal_res = "all",
                                                      start_year = 2018,
                                                      end_year = 2100,
                                                      plot_name = "regional_abs_all_BC_ts_plot",
                                                      plot_width = 8,
                                                      plot_height = 6.5,
                                                      results_dir = results_dir)

  # 4) regional "kobe" final year plot
  regional_abs_all_BC_end_plot <- BioEconomicModelPlots(dat = abs_all_BC_results_all,
                                                      spatial_res = "regional",
                                                      temporal_res = "last",
                                                      end_year = 2100,
                                                      plot_name = "regional_abs_all_BC_end_plot",
                                                      plot_width = 8,
                                                      plot_height = 6.5,
                                                      results_dir = results_dir)
}
```

## Scenario 2: Remove all bad

```{r}
# Create model input for removing all bad subsidies
abs_all_B_fleet_summary <- fleet_vessels %>%
  group_by(region, fleet) %>%
  summarize(catch = sum(catch, na.rm = T),
            bad_subs = sum(bad_ugly_subs, na.rm = T),
            fishing_KWh = sum(fishing_KWh_eez_fao_ter, na.rm = T),
            removed_subs = sum(bad_subs, na.rm = T)) %>%
  ungroup()

# Turn into a list
abs_all_B_list <- abs_all_B_fleet_summary %>%
  group_by(region) %>%
  group_split()
names(abs_all_B_list) <- colnames(bio_dat_regional)[-c(1:2)]

# Run model
abs_all_B_results <- pmap_df(list(fleet = abs_all_B_list, 
                                       region = names(abs_all_B_list),
                                       bio_param = bio_dat_regional_list),
                                  BioEconModel,
                                  end_year = 2100,
                                  return = "all")

# Extract results timeseries
abs_all_B_results_all <- abs_all_B_results %>%
  dplyr::filter(Year > 2018) %>%
  group_by(Year, Variable, Fleet) %>%
  mutate(Diff = case_when(BAU != 0 ~ (Reform - BAU)/abs(BAU),
                          TRUE ~ 0)) %>%
  ungroup() %>%
  mutate(run_id = "Absolute",
         run_name = "Capacity-enhancing subsidies")

write_csv(abs_all_B_results_all, paste0(results_dir, "abs_subs_all_B_ts.csv"))
```

  # 1) global (aggregated) timeseries plot
  abs_all_B_ts_plot <- BioEconomicModelPlots(dat = abs_all_B_results_all,
                                              spatial_res = "global",
                                              temporal_res = "all",
                                              start_year = 2018,
                                              end_year = 2100,
                                              plot_name = "abs_all_B_ts_plot",
                                              plot_width = 8,
                                              plot_height = 6.5,
                                              results_dir = results_dir)

  # 2) global (aggregated) "kobe" final year plot
  abs_all_B_end_plot <- BioEconomicModelPlots(dat = abs_all_B_results_all,
                                                      spatial_res = "global",
                                                      temporal_res = "last",
                                                      end_year = 2100,
                                                      plot_name = "abs_all_B_end_plot",
                                                      plot_width = 8,
                                                      plot_height = 6.5,
                                                      results_dir = results_dir)

  # 3) regional timeseries plot
  regional_abs_all_B_ts_plot <- BioEconomicModelPlots(dat = abs_all_B_results_all,
                                                      spatial_res = "regional",
                                                      temporal_res = "all",
                                                      start_year = 2018,
                                                      end_year = 2100,
                                                      plot_name = "regional_abs_all_B_ts_plot",
                                                      plot_width = 8,
                                                      plot_height = 6.5,
                                                      results_dir = results_dir)

  # 4) regional "kobe" final year plot
  regional_abs_all_B_end_plot <- BioEconomicModelPlots(dat = abs_all_B_results_all,
                                                      spatial_res = "regional",
                                                      temporal_res = "last",
                                                      end_year = 2100,
                                                      plot_name = "regional_abs_all_B_end_plot",
                                                      plot_width = 8,
                                                      plot_height = 6.5,
                                                      results_dir = results_dir)
}
```

## Scenario 3: Remove fuel subsidies

```{r}
# Create model input for removing all bad subsidies
abs_fuel_fleet_summary <- fleet_vessels %>%
  group_by(region, fleet) %>%
  summarize(catch = sum(catch, na.rm = T),
            bad_subs = sum(bad_ugly_subs, na.rm = T),
            fishing_KWh = sum(fishing_KWh_eez_fao_ter, na.rm = T),
            removed_subs = sum(B7_subs, na.rm = T)) %>%
  ungroup()

# Turn into a list
abs_fuel_list <- abs_fuel_fleet_summary %>%
  group_by(region) %>%
  group_split()
names(abs_fuel_list) <- colnames(bio_dat_regional)[-c(1:2)]

# Run model
abs_fuel_results <- pmap_df(list(fleet = abs_fuel_list, 
                                       region = names(abs_fuel_list),
                                       bio_param = bio_dat_regional_list),
                                  BioEconModel,
                                  end_year = 2100,
                                  return = "all")

# Extract results timeseries
abs_fuel_results_all <- abs_fuel_results %>%
  dplyr::filter(Year > 2018) %>%
  group_by(Year, Variable, Fleet) %>%
  mutate(Diff = case_when(BAU != 0 ~ (Reform - BAU)/abs(BAU),
                          TRUE ~ 0)) %>%
  ungroup() %>%
  mutate(run_id = "Absolute",
         run_name = "Fuel subsidies")

write_csv(abs_fuel_results_all, paste0(results_dir, "abs_subs_fuel_ts.csv"))
```

  # 1) global (aggregated) timeseries plot
  abs_fuel_ts_plot <- BioEconomicModelPlots(dat = abs_fuel_results_all,
                                              spatial_res = "global",
                                              temporal_res = "all",
                                              start_year = 2018,
                                              end_year = 2100,
                                              plot_name = "abs_fuel_ts_plot",
                                              plot_width = 8,
                                              plot_height = 6.5,
                                              results_dir = results_dir)

  # 2) global (aggregated) "kobe" final year plot
  abs_fuel_end_plot <- BioEconomicModelPlots(dat = abs_fuel_results_all,
                                                      spatial_res = "global",
                                                      temporal_res = "last",
                                                      end_year = 2100,
                                                      plot_name = "abs_fuel_end_plot",
                                                      plot_width = 8,
                                                      plot_height = 6.5,
                                                      results_dir = results_dir)

  # 3) regional timeseries plot
  regional_abs_fuel_ts_plot <- BioEconomicModelPlots(dat = abs_fuel_results_all,
                                                      spatial_res = "regional",
                                                      temporal_res = "all",
                                                      start_year = 2018,
                                                      end_year = 2100,
                                                      plot_name = "regional_abs_fuel_ts_plot",
                                                      plot_width = 8,
                                                      plot_height = 6.5,
                                                      results_dir = results_dir)

  # 4) regional "kobe" final year plot
  regional_abs_fuel_end_plot <- BioEconomicModelPlots(dat = abs_fuel_results_all,
                                                      spatial_res = "regional",
                                                      temporal_res = "last",
                                                      end_year = 2100,
                                                      plot_name = "regional_abs_fuel_end_plot",
                                                      plot_width = 8,
                                                      plot_height = 6.5,
                                                      results_dir = results_dir)
}
```
## Combine absolute subsidy results

```{r}
abs_results_all <- abs_all_BC_results_all %>%
  bind_rows(abs_all_B_results_all) %>%
  bind_rows(abs_fuel_results_all)
```

# Section 2: Effective subsidies

This second section presents results obtained by using effective subsidy values - based on suggestions from Roger Martini at the OECD.

```{r}
rel <- read_csv(here::here("data", "lookup-tables", "oecd_relative_effects_lookup_table.csv"))

rel_fleet_vessels <- fleet_vessels %>%
   mutate(B1_subs = B1_subs * rel$rel_effect_effort[rel$type == "B1"], 
           B2_subs = B2_subs * rel$rel_effect_effort[rel$type == "B2"],
           B3_subs = B3_subs * rel$rel_effect_effort[rel$type == "B3"],
           B4_subs = B4_subs * rel$rel_effect_effort[rel$type == "B4"],
           B5_subs = B5_subs * rel$rel_effect_effort[rel$type == "B5"], 
           B6_subs = B6_subs * rel$rel_effect_effort[rel$type == "B6"],
           B7_subs = B7_subs * rel$rel_effect_effort[rel$type == "B7"], 
           C1_subs = C1_subs * rel$rel_effect_effort[rel$type == "C1"], 
           C2_subs = C2_subs * rel$rel_effect_effort[rel$type == "C2"],
           C3_subs = C3_subs * rel$rel_effect_effort[rel$type == "C3"]) %>%
  ungroup() %>%
  mutate(bad_subs = rowSums(select(., one_of(paste0(bad_subsidy_types, "_subs")))),
         ugly_subs = rowSums(select(., one_of(paste0(ugly_subsidy_types, "_subs")))),
         bad_ugly_subs = rowSums(select(., one_of(paste0(c(bad_subsidy_types, ugly_subsidy_types), "_subs")))))
```

## Scenario 1: Remove all bad + ugly

```{r}
# Create model input for removing all bad subsidies
rel_all_BC_fleet_summary <- rel_fleet_vessels %>%
  group_by(region, fleet) %>%
  summarize(catch = sum(catch, na.rm = T),
            bad_subs = sum(bad_ugly_subs, na.rm = T),
            fishing_KWh = sum(fishing_KWh_eez_fao_ter, na.rm = T),
            removed_subs = sum(bad_ugly_subs, na.rm = T)) %>%
  ungroup()

# Turn into a list
rel_all_BC_list <- rel_all_BC_fleet_summary %>%
  group_by(region) %>%
  group_split()
names(rel_all_BC_list) <- colnames(bio_dat_regional)[-c(1:2)]

# Run model
rel_all_BC_results <- pmap_df(list(fleet = rel_all_BC_list, 
                                       region = names(rel_all_BC_list),
                                       bio_param = bio_dat_regional_list),
                                  BioEconModel,
                                  end_year = 2100,
                                  return = "all")

# Extract results timeseries
rel_all_BC_results_all <- rel_all_BC_results %>%
  dplyr::filter(Year > 2018) %>%
  group_by(Year, Variable, Fleet) %>%
  mutate(Diff = case_when(BAU != 0 ~ (Reform - BAU)/abs(BAU),
                          TRUE ~ 0)) %>%
  ungroup() %>%
  mutate(run_id = "Effective",
         run_name = "All subsidies")

write_csv(rel_all_BC_results_all, paste0(results_dir, "rel_subs_all_BC_ts.csv"))
```

  # 1) global (aggregated) timeseries plot
  rel_all_BC_ts_plot <- BioEconomicModelPlots(dat = rel_all_BC_results_all,
                                              spatial_res = "global",
                                              temporal_res = "all",
                                              start_year = 2018,
                                              end_year = 2100,
                                              plot_name = "rel_all_BC_ts_plot",
                                              plot_width = 8,
                                              plot_height = 6.5,
                                              results_dir = results_dir)

  # 2) global (aggregated) "kobe" final year plot
  rel_all_BC_end_plot <- BioEconomicModelPlots(dat = rel_all_BC_results_all,
                                                      spatial_res = "global",
                                                      temporal_res = "last",
                                                      end_year = 2100,
                                                      plot_name = "rel_all_BC_end_plot",
                                                      plot_width = 8,
                                                      plot_height = 6.5,
                                                      results_dir = results_dir)

  # 3) regional timeseries plot
  regional_rel_all_BC_ts_plot <- BioEconomicModelPlots(dat = rel_all_BC_results_all,
                                                      spatial_res = "regional",
                                                      temporal_res = "all",
                                                      start_year = 2018,
                                                      end_year = 2100,
                                                      plot_name = "regional_rel_all_BC_ts_plot",
                                                      plot_width = 8,
                                                      plot_height = 6.5,
                                                      results_dir = results_dir)

  # 4) regional "kobe" final year plot
  regional_rel_all_BC_end_plot <- BioEconomicModelPlots(dat = rel_all_BC_results_all,
                                                      spatial_res = "regional",
                                                      temporal_res = "last",
                                                      end_year = 2100,
                                                      plot_name = "regional_rel_all_BC_end_plot",
                                                      plot_width = 8,
                                                      plot_height = 6.5,
                                                      results_dir = results_dir)
}
```

## Scenario 2: Remove all bad

```{r}
# Create model input for removing all bad subsidies
rel_all_B_fleet_summary <- rel_fleet_vessels %>%
  group_by(region, fleet) %>%
  summarize(catch = sum(catch, na.rm = T),
            bad_subs = sum(bad_ugly_subs, na.rm = T),
            fishing_KWh = sum(fishing_KWh_eez_fao_ter, na.rm = T),
            removed_subs = sum(bad_subs, na.rm = T)) %>%
  ungroup()

# Turn into a list
rel_all_B_list <- rel_all_B_fleet_summary %>%
  group_by(region) %>%
  group_split()
names(rel_all_B_list) <- colnames(bio_dat_regional)[-c(1:2)]

# Run model
rel_all_B_results <- pmap_df(list(fleet = rel_all_B_list, 
                                       region = names(rel_all_B_list),
                                       bio_param = bio_dat_regional_list),
                                  BioEconModel,
                                  end_year = 2100,
                                  return = "all")

# Extract results timeseries
rel_all_B_results_all <- rel_all_B_results %>%
  dplyr::filter(Year > 2018) %>%
  group_by(Year, Variable, Fleet) %>%
  mutate(Diff = case_when(BAU != 0 ~ (Reform - BAU)/abs(BAU),
                          TRUE ~ 0)) %>%
  ungroup() %>%
  mutate(run_id = "Effective",
         run_name = "Capacity-enhancing subsidies")

write_csv(rel_all_B_results_all, paste0(results_dir, "rel_subs_all_B_ts.csv"))
```

  # 1) global (aggregated) timeseries plot
  rel_all_B_ts_plot <- BioEconomicModelPlots(dat = rel_all_B_results_all,
                                              spatial_res = "global",
                                              temporal_res = "all",
                                              start_year = 2018,
                                              end_year = 2100,
                                              plot_name = "rel_all_B_ts_plot",
                                              plot_width = 8,
                                              plot_height = 6.5,
                                              results_dir = results_dir)

  # 2) global (aggregated) "kobe" final year plot
  rel_all_B_end_plot <- BioEconomicModelPlots(dat = rel_all_B_results_all,
                                                      spatial_res = "global",
                                                      temporal_res = "last",
                                                      end_year = 2100,
                                                      plot_name = "rel_all_B_end_plot",
                                                      plot_width = 8,
                                                      plot_height = 6.5,
                                                      results_dir = results_dir)

  # 3) regional timeseries plot
  regional_rel_all_B_ts_plot <- BioEconomicModelPlots(dat = rel_all_B_results_all,
                                                      spatial_res = "regional",
                                                      temporal_res = "all",
                                                      start_year = 2018,
                                                      end_year = 2100,
                                                      plot_name = "regional_rel_all_B_ts_plot",
                                                      plot_width = 8,
                                                      plot_height = 6.5,
                                                      results_dir = results_dir)

  # 4) regional "kobe" final year plot
  regional_rel_all_B_end_plot <- BioEconomicModelPlots(dat = rel_all_B_results_all,
                                                      spatial_res = "regional",
                                                      temporal_res = "last",
                                                      end_year = 2100,
                                                      plot_name = "regional_rel_all_B_end_plot",
                                                      plot_width = 8,
                                                      plot_height = 6.5,
                                                      results_dir = results_dir)
}
```

## Scenario 3: Remove fuel subsidies

```{r}
# Create model input for removing all bad subsidies
rel_fuel_fleet_summary <- rel_fleet_vessels %>%
  group_by(region, fleet) %>%
  summarize(catch = sum(catch, na.rm = T),
            bad_subs = sum(bad_ugly_subs, na.rm = T),
            fishing_KWh = sum(fishing_KWh_eez_fao_ter, na.rm = T),
            removed_subs = sum(B7_subs, na.rm = T)) %>%
  ungroup()

# Turn into a list
rel_fuel_list <- rel_fuel_fleet_summary %>%
  group_by(region) %>%
  group_split()
names(rel_fuel_list) <- colnames(bio_dat_regional)[-c(1:2)]

# Run model
rel_fuel_results <- pmap_df(list(fleet = rel_fuel_list, 
                                       region = names(rel_fuel_list),
                                       bio_param = bio_dat_regional_list),
                                  BioEconModel,
                                  end_year = 2100,
                                  return = "all")

# Extract results timeseries
rel_fuel_results_all <- rel_fuel_results %>%
  dplyr::filter(Year > 2018) %>%
  group_by(Year, Variable, Fleet) %>%
  mutate(Diff = case_when(BAU != 0 ~ (Reform - BAU)/abs(BAU),
                          TRUE ~ 0)) %>%
  ungroup() %>%
  mutate(run_id = "Effective",
         run_name = "Fuel subsidies")

write_csv(rel_fuel_results_all, paste0(results_dir, "rel_subs_fuel_ts.csv"))
```

  # 1) global (aggregated) timeseries plot
  rel_fuel_ts_plot <- BioEconomicModelPlots(dat = rel_fuel_results_all,
                                              spatial_res = "global",
                                              temporal_res = "all",
                                              start_year = 2018,
                                              end_year = 2100,
                                              plot_name = "rel_fuel_ts_plot",
                                              plot_width = 8,
                                              plot_height = 6.5,
                                              results_dir = results_dir)

  # 2) global (aggregated) "kobe" final year plot
  rel_fuel_end_plot <- BioEconomicModelPlots(dat = rel_fuel_results_all,
                                                      spatial_res = "global",
                                                      temporal_res = "last",
                                                      end_year = 2100,
                                                      plot_name = "rel_fuel_end_plot",
                                                      plot_width = 8,
                                                      plot_height = 6.5,
                                                      results_dir = results_dir)

  # 3) regional timeseries plot
  regional_fuel_BC_ts_plot <- BioEconomicModelPlots(dat = rel_fuel_results_all,
                                                      spatial_res = "regional",
                                                      temporal_res = "all",
                                                      start_year = 2018,
                                                      end_year = 2100,
                                                      plot_name = "regional_rel_fuel_ts_plot",
                                                      plot_width = 8,
                                                      plot_height = 6.5,
                                                      results_dir = results_dir)

  # 4) regional "kobe" final year plot
  regional_rel_fuel_end_plot <- BioEconomicModelPlots(dat = rel_fuel_results_all,
                                                      spatial_res = "regional",
                                                      temporal_res = "last",
                                                      end_year = 2100,
                                                      plot_name = "regional_rel_fuel_end_plot",
                                                      plot_width = 8,
                                                      plot_height = 6.5,
                                                      results_dir = results_dir)
}
```

## Combine absolute subsidy results

```{r}
rel_results_all <- rel_all_BC_results_all %>%
  bind_rows(rel_all_B_results_all) %>%
  bind_rows(rel_fuel_results_all)
```

# Compare

```{r}
results_all <- abs_results_all %>%
  bind_rows(rel_results_all)

# Make plots
if(make_plots){

  # 1) global (aggregated) timeseries plot
  compare_ts_plot <- BioEconomicModelPlots(dat = results_all,
                                           spatial_res = "global",
                                           temporal_res = "all",
                                           start_year = 2018,
                                           end_year = 2100,
                                           plot_name = "compare_ts_plot",
                                           plot_width = 8,
                                           plot_height = 6.5,
                                           results_dir = results_dir,
                                           compare = TRUE)

  # 2) global (aggregated) "kobe" final year plot
  compare_end_plot <- BioEconomicModelPlots(dat = results_all,
                                            spatial_res = "global",
                                            temporal_res = "last",
                                            end_year = 2100,
                                            plot_name = "compare_end_plot",
                                            plot_width = 8,
                                            plot_height = 6.5,
                                            results_dir = results_dir,
                                            compare = TRUE)

  # 3) regional timeseries plot
  regional_compare_ts_plot <- BioEconomicModelPlots(dat = results_all,
                                                    spatial_res = "regional",
                                                    temporal_res = "all",
                                                    start_year = 2018,
                                                    end_year = 2100,
                                                    plot_name = "regional_compare_ts_plot",
                                                    plot_width = 8,
                                                    plot_height = 6.5,
                                                    results_dir = results_dir,
                                                    compare = TRUE)

  # 4) regional "kobe" final year plot
  regional_compare_end_plot <- BioEconomicModelPlots(dat = results_all,
                                                     spatial_res = "regional",
                                                     temporal_res = "last",
                                                     end_year = 2100,
                                                     plot_name = "regional_compare_end_plot",
                                                     plot_width = 8,
                                                     plot_height = 6.5,
                                                     results_dir = results_dir,
                                                     compare = TRUE)
}
```
```
